Proposed Solution

### 2016-11-14 Ennan-Proposal/travis.tex
intro, with news
autocommit

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
   \draw[help lines]
    \draw (2,0) rectangle (6,2); \draw (2.5,0.5) rectangle (5.5,1.5);
  \end{tikzpicture}
  \caption{System architecture of }
  \label{fig:versionSL}
\end{figure}

Necessary = 
 { Keyword, value pair "language:node_js" requires Keyword "node_js"}

where keyword "node_js" sets a version value (e.g. "node_js: 0.8")

Breaking =
  { Keyword "node_js" cannot have value <= 0 }

>>>>

\begin{figure}[!tbh]
  \centering
  \begin{tikzpicture}
    \draw (0,0) rectangle (9,4); 
    \node [align=left] at (1.5,3.5) {Breaking Rules: \\ \footnotesize ``node\_js $\le$ 0''};
    \draw (4,1) rectangle (8,3);
    \node [align=left] at (5.6,2.2) {Necessary Rules: \\ \footnotesize ``language:node\_js \\ \footnotesize $\ \land$ node\_js:version''};
  \end{tikzpicture}
  \caption{An example set of necessary and breaking rules.}
  \label{fig:versionSL}
\end{figure}
